The brightness and spatial distributions of terrestrial radio sources

### 2013-03-01 articles/Article-RFI-distribution/article-rfi-distribution.tex
Fixed suggestions by Matthew and Bryans comment on affiliation of Martin

M.~E.~Bell$^{2}$, M.~R.~Bell$^{6}$, M.~J.~Bentum$^{4}$, P.~Best$^{15}$, L.~B\^{i}rzan$^{16}$,
F.~Breitling$^{17}$, \newauthor
J.~Broderick$^{18}$, M.~Br\"uggen$^{19}$, H.~R.~Butcher$^{4,1}$, F.~de~Gasperin$^{19}$, E.~de~Geus$^{4}$,\newauthor
M.~de~Vos$^{4}$, S.~Duscha$^{4}$, J.~Eisl\"offel$^{20}$, R.~A.~Fallows$^{4}$, C.~Ferrari$^{21}$,\newauthor
W.~Frieswijk$^{4}$, M.~A.~Garrett$^{4,16}$, J.~Grie\ss{}meier$^{22}$, T.~E.~Hassall$^{18}$, A.~Horneffer$^{13}$,\newauthor
M.~Iacobelli$^{16}$, E.~Juette$^{23}$, A. ~Karastergiou$^{24}$, W.~Klijn$^{4}$, V.~I.~Kondratiev$^{4,25}$,\newauthor
M.~Kuniyoshi$^{13}$, G.~Kuper$^{4}$, J.~van~Leeuwen$^{4,26}$, M.~Loose$^{4}$, P.~Maat$^{4}$,\newauthor
G.~Maccario$^{21}$, G.~Mann$^{17}$, J.~P.~McKean$^{4}$, H.~Meulman$^{4}$, M.~J.~Norden$^{4}$, 
\newauthor
E.~Orru$^{4}$, H.~Paas$^{27}$, M.~Pandey-Pommier$^{28}$, R.~Pizzo$^{4}$, A.~G.~Polatidis$^{4}$,\newauthor
D.~Rafferty$^{16}$, W.~Reich$^{13}$, R.~van~Nieuwpoort$^{4}$, H.~R\"ottgering$^{16}$, \newauthor
A.~M.~M.~Scaife$^{18}$, J.~Sluman$^{4}$, O.~Smirnov$^{29,30}$, C.~Sobey$^{13}$, M.~Tagger$^{22}$,\newauthor
Y.~Tang$^{4}$, C.~Tasse$^{11}$, S.~ter~Veen$^{31}$, C.~Toribio$^{4}$, R.~Vermeulen$^{4}$, C.~Vocks$^{17}$,\newauthor
R.~J.~van~Weeren$^{10}$, M.~W.~Wise$^{4,26}$, O.~Wucknitz$^{32,13}$

@@

$^{15}$Institute for Astronomy, University of Edinburgh, Royal Observatory of Edinburgh, Blackford Hill, Edinburgh EH9 3HJ, UK \\
$^{16}$Leiden Observatory, Leiden University, PO Box 9513, 2300 RA Leiden, The Netherlands \\
$^{17}$Leibniz-Institut f\"{u}r Astrophysik Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany \\
$^{18}$School of Physics and Astronomy, University of Southampton, Southampton, SO17 1BJ, UK \\
$^{19}$University of Hamburg, Gojenbergsweg 112, 21029 Hamburg, Germany \\
$^{20}$Th\"{u}ringer Landessternwarte, Sternwarte 5, D-07778 Tautenburg, Germany \\
$^{21}$Laboratoire Lagrange, UMR7293, Universit\`{e} de Nice Sophia-Antipolis, CNRS, Observatoire de la C\'{o}te d'Azur, 06300 Nice, France \\
$^{22}$Laboratoire de Physique et Chimie de l' Environnement et de l' Espace, LPC2E UMR 7328 CNRS, 45071 Orl\'{e}ans Cedex 02, France \\
$^{23}$Astronomisches Institut der Ruhr-Universit\"{a}t Bochum, Universitaetsstrasse 150, 44780 Bochum, Germany \\
$^{24}$Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH \\
$^{25}$Astro Space Center of the Lebedev Physical Institute, Profsoyuznaya str. 84/32, Moscow 117997, Russia \\
$^{26}$Astronomical Institute 'Anton Pannekoek', University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands \\
$^{27}$Center for Information Technology (CIT), University of Groningen, The Netherlands \\
$^{28}$Centre de Recherche Astrophysique de Lyon, Observatoire de Lyon, 9 av Charles Andr\'{e}, 69561 Saint Genis Laval Cedex, France \\
$^{29}$Centre for Radio Astronomy Techniques \& Technologies (RATT), Department of Physics and Elelctronics, Rhodes University, PO Box 94, Grahamstown 6140, South Africa \\
$^{30}$SKA South Africa, 3rd Floor, The Park, Park Road, Pinelands, 7405, South Africa \\
$^{31}$Department of Astrophysics/IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands \\
$^{32}$Argelander-Institut f\"{u}r Astronomie, University of Bonn, Auf dem H\"{u}gel 71, 53121, Bonn, Germany

>>>>

M.~E.~Bell$^{2,15}$, M.~R.~Bell$^{6}$, M.~J.~Bentum$^{4}$, P.~Best$^{16}$, L.~B\^{i}rzan$^{17}$, F.~Breitling$^{18}$,\newauthor
J.~Broderick$^{19}$, M.~Br\"uggen$^{20}$, H.~R.~Butcher$^{4,1}$, F.~de~Gasperin$^{20}$, E.~de~Geus$^{4}$,\newauthor
M.~de~Vos$^{4}$, S.~Duscha$^{4}$, J.~Eisl\"offel$^{21}$, R.~A.~Fallows$^{4}$, C.~Ferrari$^{22}$,\newauthor
W.~Frieswijk$^{4}$, M.~A.~Garrett$^{4,17}$, J.~Grie\ss{}meier$^{23}$, T.~E.~Hassall$^{19}$, A.~Horneffer$^{13}$,\newauthor
M.~Iacobelli$^{17}$, E.~Juette$^{24}$, A. ~Karastergiou$^{25}$, W.~Klijn$^{4}$, V.~I.~Kondratiev$^{4,26}$,\newauthor
M.~Kuniyoshi$^{13}$, G.~Kuper$^{4}$, J.~van~Leeuwen$^{4,27}$, M.~Loose$^{4}$, P.~Maat$^{4}$,\newauthor
G.~Macario$^{22}$, G.~Mann$^{18}$, J.~P.~McKean$^{4}$, H.~Meulman$^{4}$, M.~J.~Norden$^{4}$,\newauthor
E.~Orru$^{4}$, H.~Paas$^{28}$, M.~Pandey-Pommier$^{29}$, R.~Pizzo$^{4}$, A.~G.~Polatidis$^{4}$,\newauthor
D.~Rafferty$^{17}$, W.~Reich$^{13}$, R.~van~Nieuwpoort$^{4}$, H.~R\"ottgering$^{17}$,\newauthor
A.~M.~M.~Scaife$^{19}$, J.~Sluman$^{4}$, O.~Smirnov$^{30,31}$, C.~Sobey$^{13}$, M.~Tagger$^{23}$,\newauthor
Y.~Tang$^{4}$, C.~Tasse$^{11}$, S.~ter~Veen$^{32}$, C.~Toribio$^{4}$, R.~Vermeulen$^{4}$, C.~Vocks$^{18}$,\newauthor
R.~J.~van~Weeren$^{10}$, M.~W.~Wise$^{4,27}$, O.~Wucknitz$^{33,13}$

@@

$^{15}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia \\
$^{16}$Institute for Astronomy, University of Edinburgh, Royal Observatory of Edinburgh, Blackford Hill, Edinburgh EH9 3HJ, UK \\
$^{17}$Leiden Observatory, Leiden University, PO Box 9513, 2300 RA Leiden, The Netherlands \\
$^{18}$Leibniz-Institut f\"{u}r Astrophysik Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany \\
$^{19}$School of Physics and Astronomy, University of Southampton, Southampton, SO17 1BJ, UK \\
$^{20}$University of Hamburg, Gojenbergsweg 112, 21029 Hamburg, Germany \\
$^{21}$Th\"{u}ringer Landessternwarte, Sternwarte 5, D-07778 Tautenburg, Germany \\
$^{22}$Laboratoire Lagrange, UMR7293, Universit\`{e} de Nice Sophia-Antipolis, CNRS, Observatoire de la C\'{o}te d'Azur, 06300 Nice, France \\
$^{23}$Laboratoire de Physique et Chimie de l' Environnement et de l' Espace, LPC2E UMR 7328 CNRS, 45071 Orl\'{e}ans Cedex 02, France \\
$^{24}$Astronomisches Institut der Ruhr-Universit\"{a}t Bochum, Universitaetsstrasse 150, 44780 Bochum, Germany \\
$^{25}$Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH \\
$^{26}$Astro Space Center of the Lebedev Physical Institute, Profsoyuznaya str. 84/32, Moscow 117997, Russia \\
$^{27}$Astronomical Institute 'Anton Pannekoek', University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands \\
$^{28}$Center for Information Technology (CIT), University of Groningen, The Netherlands \\
$^{29}$Centre de Recherche Astrophysique de Lyon, Observatoire de Lyon, 9 av Charles Andr\'{e}, 69561 Saint Genis Laval Cedex, France \\
$^{30}$Centre for Radio Astronomy Techniques \& Technologies (RATT), Department of Physics and Elelctronics, Rhodes University, PO Box 94, Grahamstown 6140, South Africa \\
$^{31}$SKA South Africa, 3rd Floor, The Park, Park Road, Pinelands, 7405, South Africa \\
$^{32}$Department of Astrophysics/IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands \\
$^{33}$Argelander-Institut f\"{u}r Astronomie, University of Bonn, Auf dem H\"{u}gel 71, 53121, Bonn, Germany
